### 2016-02-01 Projects/DelCo_2014_2015/Reports/FDS_Validation_Report/TeX_Files/FDS_Exp_Description_Report.tex
DelCo_2014_2015: Added folder for FDS validation report

\input{../../../Bibliography/commoncommands}

@@

\headerB{
Delco 2014
}

\headerC{
\flushright{
Daniel Madrzykowski \\
Craig G. Weinschenk \\
Kristopher J. Overholt \\
{\em Fire Research Division \\
Engineering Laboratory \\
Gaithersburg, Maryland, USA} \\ }
}

@@

\flushright{
\includegraphics[width=2.in]{../../../Bibliography/nistident_flright_vec} \\[.3in]
}

@@

\subsection{Construction}
\label{sec:Construction}
The building was composed of concrete walls, as shown in Fig.~\ref{fig:EL_Logo_Example}.

\begin{figure}[!ht]
\includegraphics[width=2in]{../Figures/el_logo_small}
\caption{NIST Engineering Laboratory}
\label{fig:EL_Logo_Example}
\end{figure}

\section{Fuel Load}

\chapter{Results}
\label{chap:Results}

\section{Hose Flow Tests}

\subsection{DNXAXX}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXAXX_BDP_A7}
\caption{Velocity at exterior Door A, Test HOSE\_DNXAXX}
\label{fig:HOSE_DNXAXX_BDP_A7}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXAXX_BDP_A8}
\caption{Velocity at exterior Door C\_West, Test HOSE\_DNXAXX}
\label{fig:HOSE_DNXAXX_BDP_A8}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXAXX_BDP_A9}
\caption{Velocity at exterior Door C\_East, Test HOSE\_DNXAXX}
\label{fig:HOSE_DNXAXX_BDP_A9}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXAXX_HOSE}
\caption{Hose pressure, Test HOSE\_DNXAXX}
\label{fig:HOSE_DNXAXX_HOSE}
\end{figure}

\clearpage

\subsection{DNXOXF}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXOXF_BDP_A7}
\caption{Velocity at exterior Door A, Test HOSE\_DNXOXF}
\label{fig:HOSE_DNXOXF_BDP_A7}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXOXF_BDP_A8}
\caption{Velocity at exterior Door C\_West, Test HOSE\_DNXOXF}
\label{fig:HOSE_DNXOXF_BDP_A8}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXOXF_BDP_A9}
\caption{Velocity at exterior Door C\_East, Test HOSE\_DNXOXF}
\label{fig:HOSE_DNXOXF_BDP_A9}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXOXF_HOSE}
\caption{Hose pressure, Test HOSE\_DNXOXF}
\label{fig:HOSE_DNXOXF_HOSE}
\end{figure}

\clearpage

\subsection{DSXAXF}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXAXF_BDP_A7}
\caption{Velocity at exterior Door A, Test HOSE\_DSXAXF}
\label{fig:HOSE_DSXAXF_BDP_A7}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXAXF_BDP_A8}
\caption{Velocity at exterior Door C\_West, Test HOSE\_DSXAXF}
\label{fig:HOSE_DSXAXF_BDP_A8}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXAXF_BDP_A9}
\caption{Velocity at exterior Door C\_East, Test HOSE\_DSXAXF}
\label{fig:HOSE_DSXAXF_BDP_A9}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXAXF_HOSE}
\caption{Hose pressure, Test HOSE\_DSXAXF}
\label{fig:HOSE_DSXAXF_HOSE}
\end{figure}

\clearpage

\subsection{DSXOXF}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXOXF_BDP_A7}
\caption{Velocity at exterior Door A, Test HOSE\_DSXOXF}
\label{fig:HOSE_DSXOXF_BDP_A7}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXOXF_BDP_A8}
\caption{Velocity at exterior Door C\_West, Test HOSE\_DSXOXF}
\label{fig:HOSE_DSXOXF_BDP_A8}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXOXF_BDP_A9}
\caption{Velocity at exterior Door C\_East, Test HOSE\_DSXOXF}
\label{fig:HOSE_DSXOXF_BDP_A9}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXOXF_HOSE}
\caption{Hose pressure, Test HOSE\_DSXOXF}
\label{fig:HOSE_DSXOXF_HOSE}
\end{figure}

\clearpage

\subsection{IXAOXX}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXAOXX_BDP_A6}
\caption{Velocity at interior Door CD, Test HOSE\_IXAOXX}
\label{fig:HOSE_IXAOXX_BDP_A6}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXAOXX_BDP_A7}
\caption{Velocity at exterior Door A, Test HOSE\_IXAOXX}
\label{fig:HOSE_IXAOXX_BDP_A7}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXAOXX_BDP_A8}
\caption{Velocity at exterior Door C\_West, Test HOSE\_IXAOXX}
\label{fig:HOSE_IXAOXX_BDP_A8}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXAOXX_BDP_A9}
\caption{Velocity at exterior Door C\_East, Test HOSE\_IXAOXX}
\label{fig:HOSE_IXAOXX_BDP_A9}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXAOXX_HOSE}
\caption{Hose pressure, Test HOSE\_IXAOXX}
\label{fig:HOSE_IXAOXX_HOSE}
\end{figure}

\clearpage

\subsection{IXXAXX}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXXAXX_BDP_A6}
\caption{Velocity at interior Door CD, Test HOSE\_IXXAXX}
\label{fig:HOSE_IXXAXX_BDP_A6}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXXAXX_BDP_A7}
\caption{Velocity at exterior Door A, Test HOSE\_IXXAXX}
\label{fig:HOSE_IXXAXX_BDP_A7}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXXAXX_BDP_A8}
\caption{Velocity at exterior Door C\_West, Test HOSE\_IXXAXX}
\label{fig:HOSE_IXXAXX_BDP_A8}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXXAXX_BDP_A9}
\caption{Velocity at exterior Door C\_East, Test HOSE\_IXXAXX}
\label{fig:HOSE_IXXAXX_BDP_A9}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXXAXX_HOSE}
\caption{Hose pressure, Test HOSE\_IXXAXX}
\label{fig:HOSE_IXXAXX_HOSE}
\end{figure}

\clearpage

\section{Fire Tests}

\subsection{FIRE\_FA2S1C1NCX1\_1}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_BDP_A7}
\caption{Velocity at exterior Door A, Test FIRE\_FA2S1C1NCX1\_1}
\label{fig:FIRE_FA2S1C1NCX1_1_BDP_A7}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A7}
\caption{Temperature at exterior Door A, Test FIRE\_FA2S1C1NCX1\_1}
\label{fig:FIRE_FA2S1C1NCX1_1_TC_A7}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_BDP_A8}
\caption{Velocity at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_1}
\label{fig:FIRE_FA2S1C1NCX1_1_BDP_A8}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A8}
\caption{Temperature at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_1}
\label{fig:FIRE_FA2S1C1NCX1_1_TC_A8}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_BDP_A9}
\caption{Velocity at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_1}
\label{fig:FIRE_FA2S1C1NCX1_1_BDP_A9}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A9}
\caption{Temperature at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_1}
\label{fig:FIRE_FA2S1C1NCX1_1_TC_A9}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_GAS}
\caption{Gas Concentration, Test FIRE\_FA2S1C1NCX1\_1}
\label{fig:FIRE_FA2S1C1NCX1_1_GAS}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_HF}
\caption{Heat Flux, Test FIRE\_FA2S1C1NCX1\_1}
\label{fig:FIRE_FA2S1C1NCX1_1_HF}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A1}
\caption{Temperature at TC Tree A1, Room A, Test FIRE\_FA2S1C1NCX1\_1}
\label{fig:FIRE_FA2S1C1NCX1_1_TC_A1}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A2}
\caption{Temperature at TC Tree A2, Room A, Test FIRE\_FA2S1C1NCX1\_1}
\label{fig:FIRE_FA2S1C1NCX1_1_TC_A2}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A3}
\caption{Temperature at TC Tree A3, Room B, Test FIRE\_FA2S1C1NCX1\_1}
\label{fig:FIRE_FA2S1C1NCX1_1_TC_A3}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A4}
\caption{Temperature at TC Tree A4, Room C, Test FIRE\_FA2S1C1NCX1\_1}
\label{fig:FIRE_FA2S1C1NCX1_1_TC_A4}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A5}
\caption{Temperature at TC Tree A5, Room C, Test FIRE\_FA2S1C1NCX1\_1}
\label{fig:FIRE_FA2S1C1NCX1_1_TC_A5}
\end{figure}

\clearpage

\subsection{FIRE\_FA2S1C1NCX1\_2}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_BDP_A7}
\caption{Velocity at exterior Door A, Test FIRE\_FA2S1C1NCX1\_2}
\label{fig:FIRE_FA2S1C1NCX1_2_BDP_A7}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A7}
\caption{Temperature at exterior Door A, Test FIRE\_FA2S1C1NCX1\_2}
\label{fig:FIRE_FA2S1C1NCX1_2_TC_A7}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_BDP_A8}
\caption{Velocity at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_2}
\label{fig:FIRE_FA2S1C1NCX1_2_BDP_A8}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A8}
\caption{Temperature at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_2}
\label{fig:FIRE_FA2S1C1NCX1_2_TC_A8}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_BDP_A9}
\caption{Velocity at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_2}
\label{fig:FIRE_FA2S1C1NCX1_2_BDP_A9}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A9}
\caption{Temperature at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_2}
\label{fig:FIRE_FA2S1C1NCX1_2_TC_A9}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_GAS}
\caption{Gas Concentration, Test FIRE\_FA2S1C1NCX1\_2}
\label{fig:FIRE_FA2S1C1NCX1_2_GAS}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_HF}
\caption{Heat Flux, Test FIRE\_FA2S1C1NCX1\_2}
\label{fig:FIRE_FA2S1C1NCX1_2_HF}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A1}
\caption{Temperature at TC Tree A1, Room A, Test FIRE\_FA2S1C1NCX1\_2}
\label{fig:FIRE_FA2S1C1NCX1_2_TC_A1}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A2}
\caption{Temperature at TC Tree A2, Room A, Test FIRE\_FA2S1C1NCX1\_2}
\label{fig:FIRE_FA2S1C1NCX1_2_TC_A2}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A3}
\caption{Temperature at TC Tree A3, Room B, Test FIRE\_FA2S1C1NCX1\_2}
\label{fig:FIRE_FA2S1C1NCX1_2_TC_A3}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A4}
\caption{Temperature at TC Tree A4, Room C, Test FIRE\_FA2S1C1NCX1\_2}
\label{fig:FIRE_FA2S1C1NCX1_2_TC_A4}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A5}
\caption{Temperature at TC Tree A5, Room C, Test FIRE\_FA2S1C1NCX1\_2}
\label{fig:FIRE_FA2S1C1NCX1_2_TC_A5}
\end{figure}

\clearpage

\subsection{FIRE\_FA2S1C1NCX1\_3}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_BDP_A7}
\caption{Velocity at exterior Door A, Test FIRE\_FA2S1C1NCX1\_3}
\label{fig:FIRE_FA2S1C1NCX1_3_BDP_A7}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A7}
\caption{Temperature at exterior Door A, Test FIRE\_FA2S1C1NCX1\_3}
\label{fig:FIRE_FA2S1C1NCX1_3_TC_A7}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_BDP_A8}
\caption{Velocity at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_3}
\label{fig:FIRE_FA2S1C1NCX1_3_BDP_A8}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A8}
\caption{Temperature at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_3}
\label{fig:FIRE_FA2S1C1NCX1_3_TC_A8}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_BDP_A9}
\caption{Velocity at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_3}
\label{fig:FIRE_FA2S1C1NCX1_3_BDP_A9}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A9}
\caption{Temperature at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_3}
\label{fig:FIRE_FA2S1C1NCX1_3_TC_A9}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_GAS}
\caption{Gas Concentration, Test FIRE\_FA2S1C1NCX1\_3}
\label{fig:FIRE_FA2S1C1NCX1_3_GAS}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_HF}
\caption{Heat Flux, Test FIRE\_FA2S1C1NCX1\_3}
\label{fig:FIRE_FA2S1C1NCX1_3_HF}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A1}
\caption{Temperature at TC Tree A1, Room A, Test FIRE\_FA2S1C1NCX1\_3}
\label{fig:FIRE_FA2S1C1NCX1_3_TC_A1}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A2}
\caption{Temperature at TC Tree A2, Room A, Test FIRE\_FA2S1C1NCX1\_3}
\label{fig:FIRE_FA2S1C1NCX1_3_TC_A2}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A3}
\caption{Temperature at TC Tree A3, Room B, Test FIRE\_FA2S1C1NCX1\_3}
\label{fig:FIRE_FA2S1C1NCX1_3_TC_A3}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A4}
\caption{Temperature at TC Tree A4, Room C, Test FIRE\_FA2S1C1NCX1\_3}
\label{fig:FIRE_FA2S1C1NCX1_3_TC_A4}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A5}
\caption{Temperature at TC Tree A5, Room C, Test FIRE\_FA2S1C1NCX1\_3}
\label{fig:FIRE_FA2S1C1NCX1_3_TC_A5}
\end{figure}

\clearpage

\chapter{Conclusions}
\label{chap:Conclusions}

>>>>

\input{../../../../../Bibliography/commoncommands}

@@

\headerB{
Overview of Fire Model Validation Experiments in Residential Scale Structures
}

\headerC{
\flushright{
Joseph Willi \\
Kevin McGrattan \\
Randall McDermott \\
Craig Weinschenk \\
{\em Fire Research Division \\
Engineering Laboratory \\
Gaithersburg, Maryland, USA} \\ }
}

@@

\flushright{
\includegraphics[width=2.in]{../../../../../Bibliography/nistident_flright_vec} \\[.3in]
}

@@

\subsection{Construction}
\label{sec:Construction}

\section{Instrumentation}
\label{sec:Instrumentation}

\chapter{Experimental Procedure}
\label{chap:Experimental_Procedure}

### 2016-02-01 Projects/DelCo_2014_2015/Reports/Hose_Stream_Report/TeX_Files/DelCo_Hose_Stream_Tests.tex
DelCo_2014_2015: Added folder for FDS validation report

\begin{figure}[!ht]
\includegraphics[width=6in]{../Pictures/TJI_support}
\caption[TJI-constructred ceiling/floor support of the West Structure.]{Ceiling and floor support of the West Structure composed of wood truss joist I-beams. View is of the east side of the structure.}
\label{fig:TJI}
\end{figure}
\FloatBarrier

>>>>

\begin{figure}[!ht]
\includegraphics[width=6in]{../Pictures/TJI_support}
\caption[TJI-constructed ceiling/floor support of the West Structure.]{Ceiling and floor support of the West Structure composed of wood truss joist I-beams. View is of the east side of the structure.}
\label{fig:TJI}
\end{figure}
\FloatBarrier
